---
title: "General Set-Up and Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{General Set-Up and Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

file_loc = "C:/Users/meowy/OneDrive/Desktop/fbm_data_subset"
```

#### This vignette will walk you through the general set-up and usage of the metamessengr package. 

```{r setup}
library(metamessengr)
```

##### Selecting and Reading in Data

The first and most important function of the package is the `mess_sentiment()` function. This function allows one to parse through Facebook's JSON formatted Messenger data and select the most important information - who sent what, what did they send, and when did they send it.

The function is recursive, so all that needs to be specified is the folder that contains all of the downloaded and unzipped data from Facebook. The conversations will be in a file called `"/inbox`. The output will be a data frame with 4 variables: the timestamp, the sender, the content, and which chat it was sent to.

```{r}
## Enter your file location
me <- mess_selection(file_loc = file_loc)

me
```

##### Cleaning Selected Data

The newly imported data needs to be cleaned. This can be done piece-wise, through the use of the `clean_mess_text()` and `clean_mess_time()` functions, or it can be done all at once using `clean_mess_all()`. For most situations, it's best to use `clean_mess_all()` to reduce the potential for user error.

Stop words ("as", "the", "a", etc.) are generally removed before text analysis, as they do not contribute meaningfully to context. 

```{r}

```
